An Analysis of Security Vulnerabilities in Container Images for Scientific Data Analysis

### 2020-10-26 paper.tex
typos

\href{https://github.com/singularityhub/stools}{Singularity Tools} (Stools)
are an extension of Clair for Singularity images. Stools
exports Singularity images to \texttt{tar.gz} format, acting as a single layer Docker image
to circumvent the Docker-specific requirements in the Clair API.
In our experiments, we used Singularity Tools version 3.2.1 through Docker
image
\texttt{vanessa/stools-clair:v3.2.1}.
% , which is using another Docker
% image \texttt{arminc/clair-db:latest} for referring to vulnerability feed.
Since Stools uses Clair internally for scanning, vulnerability databases used
by Stools are same as mentioned for Clair.
To scan Singularity images, we followed the steps mentioned in the
\href{https://github.com/singularityhub/stools}{Stools documentation}.

@@

Many vulnerabilities in region \textbf{3} and \textbf{4} are from images
based on Ubuntu 14.04. In the Ubuntu CVE tracker database used by Clair and
Anchore, there are two entries for Ubuntu 14.04: one for LTS (Long-Term
Support), a Ubuntu release with 5 years of technical support, and another one
for ESM (Extended Security Maintenance), a release that provides security
patches beyond the 5 years covered by LTS. Although all the scanned images
are LTS, Clair refers to the ESM database entry while Anchore and Vuls refer to the
LTS database entry. The vulnerabilities present in region \textbf{3} due to
this discrepancy are incorrectly missed by Anchore and Vuls: they have been
detected in ESM but were already present in LTS. The vulneratibilities in
region \textbf{4} are incorrectly missed by Clair: they have been fixed in
ESM but are still present in LTS.

>>>>

\href{https://github.com/singularityhub/stools}{Singularity Tools} (Stools)
are an extension of Clair for Singularity images. Stools
exports Singularity images to \texttt{tar.gz} format, acting as a single layer Docker image
to circumvent the Docker-specific requirements in the Clair API.
In our experiments, we used Singularity Tools version 3.2.1 through Docker
image
\texttt{vanessa/stools-clair:v3.2.1}.
% , which is using another Docker
% image \texttt{arminc/clair-db:latest} for referring to vulnerability feed.
Since Stools uses Clair internally for scanning, the vulnerability databases used
by Stools are the same as mentioned for Clair.
To scan Singularity images, we followed the steps mentioned in the
\href{https://github.com/singularityhub/stools}{Stools documentation}.

@@

Many vulnerabilities in region \textbf{3} and \textbf{4} are from images
based on Ubuntu 14.04. In the Ubuntu CVE tracker database used by Clair and
Anchore, there are two entries for Ubuntu 14.04: one for LTS (Long-Term
Support), a Ubuntu release with 5 years of technical support, and another one
for ESM (Extended Security Maintenance), a release that provides security
patches beyond the 5 years covered by LTS. Although all the scanned images
are LTS, Clair refers to the ESM database entry while Anchore and Vuls refer to the
LTS database entry. The vulnerabilities present in region \textbf{3} due to
this discrepancy are incorrectly missed by Anchore and Vuls: they have been
detected in ESM but were already present in LTS. The vulnerabilities in
region \textbf{4} are incorrectly missed by Clair: they have been fixed in
ESM but are still present in LTS.
